MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38 - Model Selection

### 2020-04-07 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_SALMON_GRCh38.Rmd
fix header

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38.Rmd",
                                 parentId ="syn21435176",
                                 folderName = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38")
```

@@

thisFileName <- 'MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38.Rmd'

>>>>

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_SALMON_GRCh38.Rmd",
                                 parentId ="syn21435176",
                                 folderName = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38")
```

@@

thisFileName <- 'MSSM-Penn-Pitt_ACC_DLPFC_SALMON_GRCh38.Rmd'
